Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-02-27 latex/MPP21/paper.tex
added table of algs and started to clean up references
working on first plots

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} }

@@

\author{\IEEEauthorblockN{Grey Ballard}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{ballard@wfu.edu}}
\and
\IEEEauthorblockN{Jack Weissenberger}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.) \GB{?}} \\
\textit{Capital One \GB{?}}\\
Richmond, VA \\
email address or ORCID}
\and
\IEEEauthorblockN{Luoping\GB{?} Zhang}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{zhanl317@wfu.edu}}
}

@@

@@

>>>>

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}

% for subfigures
\usepackage[caption=false,font=footnotesize]{subfig}

% for scientific notation like 1e-8
\usepackage{siunitx}
\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} } 
\newcommand{\dims}[1]{\langle #1 \rangle}

\newcommand{\datafile}{}

@@

\author{\IEEEauthorblockN{Grey Ballard}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{ballard@wfu.edu}}
\and
\IEEEauthorblockN{Jack Weissenberger}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{jack.weissenberger@gmail.com}}
\and
\IEEEauthorblockN{Luoping\GB{?} Zhang}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{zhanl317@wfu.edu}}
}

@@

\begin{table}
\centering
\caption{Properties of Arbitrary Precision Approximating Algorithms  \\ Speedup and Error are computed assuming 1 recursive step}
\label{tab:algs}
\begin{tabular}{| c | c c c | c c c |} 
\hline
\textbf{Ref} & \textbf{Dims} & \textbf{Rank} & \textbf{Speedup} & $\mathbf{\sigma}$ & $\mathbf{\varphi}$ & \textbf{Error} \\
\hline
- & $\dims{2,2,2}$ & 8 & - & 1 & 0 & \num{1.2e-7} \\
\hline
\cite{BCRL79} & $\dims{3,2,2}$ & 10 & $20\%$ & 1 & 1 & \num{3.5e-4} \\
\cite{Smirnov13} & $\dims{4,2,2}$ & 13 & $23\%$ & 1 & 2 & \num{4.9e-3} \\
\cite{Smirnov13} & $\dims{3,3,2}$ & 14 & $29\%$ & 1 & 3 & \num{1.9e-2} \\
\cite{Smirnov13} & $\dims{5,2,2}$ & 16 & $25\%$ & 1 & 3 & \num{1.9e-2} \\
\cite{Smirnov13} & $\dims{3,3,3}$ & 20 & $35\%$ & 1 & 6 & \num{1.0e-1} \\
\cite{Schonhage81} & $\dims{3,3,3}$ & 21 & $29\%$ & 1 & 2 & \num{4.9e-3} \\
\cite{Smirnov15} & $\dims{7,2,2}$ & 22 & $27\%$ & 1 & 5 & \num{7.0e-2} \\
\cite{Smirnov13} & $\dims{4,4,2}$ & 24 & $33\%$ & 1 & 3 & \num{1.9e-2} \\
\cite{Smirnov16} & $\dims{4,3,3}$ & 27 & $33\%$ & 1 & 3 & \num{1.9e-2} \\
\cite{Smirnov18} & $\dims{5,5,2}$ & 37 & $35\%$ & 1 & 3 & \num{1.9e-2} \\
\cite{Smirnov14} & $\dims{4,4,4}$ & 46 & $39\%$ & 1 & 3 & \num{1.9e-2} \\
\cite{Smirnov18} & $\dims{5,5,5}$ & 90 & $39\%$ & 1 & 3 & \num{1.9e-2} \\
\hline
\end{tabular}
\end{table}

\GB{specify formula for speedup and error values...}

@@

\begin{figure}
\subfloat[One thread]{
\renewcommand{\datafile}{data/NNtime_1t.dat}
\input{plots/reltime}
\label{fig:NNreltime_seq}}
\hfill
\subfloat[Twelve threads]{
csv files should have columns n,DGEMM,Bini,... and row for each dim
\label{fig:NNreltime_par}}
\caption{Network training time relative to using classical matrix multiplication}
\label{fig:NNreltime}
\end{figure}
